---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Temperature, species identity and morphological traits predict carbonate excretion and mineralogy in tropical reef fishes

[![License: MIT + file LICENSE](https://img.shields.io/badge/License-MIT + file LICENSE-blue.svg)](https://choosealicense.com/licenses/mit/)

The goal of this project is to reproduce all analyses, figures, and tables of the paper

> Title: Temperature, species identity and morphological traits predict carbonate excretion and mineralogy in tropical reef fishes.
>
> Authors: Ghilardi M, Salter MA, Parravicini V, Ferse SCA, Rixen T, Wild C, Birkicht M, Perry CT, Berry A, Wilson RW, Mouillot D, Bejarano S 

## Content

This repository is structured as follow:

- [:file\_folder: data/](https://github.com/mattiaghilardi/FishCaCO3Model/tree/master/data):
contains all data used in the analyses.

- [:file\_folder: analysis/](https://github.com/mattiaghilardi/FishCaCO3Model/tree/master/analysis):
contains R scripts to reproduce the analyses.

- [:file\_folder: outputs/](https://github.com/mattiaghilardi/FishCaCO3Model/tree/master/outputs):
contains all the outputs created during the analyses, including figures, tables and models.

- [:file\_folder: R/](https://github.com/mattiaghilardi/FishCaCO3Model/tree/master/R):
contains R functions developed mainly for this project.

- [:file\_folder: man/](https://github.com/mattiaghilardi/FishCaCO3Model/tree/master/man):
contains help files of R functions.

- [:page_facing_up: DESCRIPTION](https://github.com/mattiaghilardi/FishCaCO3Model/blob/master/DESCRIPTION):
contains project metadata.

- [:page_facing_up: make.R](https://github.com/mattiaghilardi/FishCaCO3Model/blob/master/make.R):
main R script to run the entire project.

## Instructions

- Clone this repository (for those not familiar with GitHub, click on the green button `Code` on the project main page on GitHub and then on `Download ZIP` to download the entire repository, thus unzip it).

- Open the `.Rproj` file in RStudio or open an R session with working directory set to the root of the project.

- Reproduce the entire project by running:

```{r eval = FALSE}
source("make.R")
```

## Notes

- When this project is launched, the appropriate version of `renv` should be automatically downloaded and installed into the project library. After this has completed, running `source("make.R")` will first restore the project library locally on the machine.
- All required packages and R functions will be loaded.
- Some steps of the workflow might take time.
- The project depends on parallel computation and uses 4 cores. It is possible to change the number of cores in the `make.R` file under `Global options`. On Windows it must be set to 1 and some steps might take very long.

## Working environment

```{r echo=FALSE}
sessionInfo()
```
